Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-13 mtjournal.tex
Mari's comments on paradigm section

\item[Decompositions]: we consider syntactic decompositions of the
  following types.

@@

      \textrm{Head}\right\rangle$ here, every tuple includes two words

@@

      \right\rangle$ the tuple is the word plus the label of the arc

@@

      \right\rangle$ each tuple here is the dependency relation plus

@@

      \right\rangle$ here, drops the arc-label. This decomposition

@@

    \item[1g,2g] these decompositions are syntactically-null.  They

@@

\item[Forest size] Although the parser can generate considerably more,
  we consider forests of size 1 and of size 50.
\item[Forest confidence] An expectation requires a probability

@@

\item[score combination]: We consider three possible methods for

@@

    the tree, ad then computes a global $F$ score.

@@

To avoid this conflation, on the HTER corpora we report correlations
on $\bar{\mu}(m)$
and $\bar{\mu}(\textrm{HTER})$ (rather than measure $m$ and HTER), where
$\bar{\mu}$ represents mean-removal:
\begin{equation}
  \label{eq:meansub}
  \bar{\mu}(m(t_i)) = m(t_i) - \sum_{j=1}^I\frac{m(t_j)}{I}
\end{equation}
Mean-removal lowers the correlation $r$ values reported but ensures
that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.
\footnote{ Previous work \cite{kahn08metricsmatr} reported HTER
  correlations against pairwise differences among translation segments
  derived from the same source segment. Those results are similar to
  those reported here. However, we believe that pairwise differences
  introduce problems with the independence assumptions in
  the Pearson's $r$ tests, and we use mean-removal
  throughout this work instead.}

When reporting HTER correlations per-sentence, we use length-weighted
correlation, since unweighted correlations effectively puts too much
emphasis on short sentences.  We do not weight for length for the
per-document correlations in section~\ref{sec:hter1}, because we
assume documents to be equally important (regardless of length).

>>>>

\item[Decompositions.] We consider syntactic decompositions of the
  following types:

@@

      \textrm{Head}\right\rangle$ Here, every tuple includes two words

@@

      \right\rangle$ The tuple is the word plus the label of the arc

@@

      \right\rangle$ Each tuple here is the dependency relation plus

@@

      \right\rangle$ Here, drops the arc-label. This decomposition

@@

    \item[1g,2g] These decompositions are syntactically-null.  They

@@

\item[Size of $n$-best list.] Although the parser can generate considerably more,
  we consider $n$-best lists  of size 1 and of size 50.
\item[Confidence of $n$-best list.] An expectation requires a probability

@@

\item[Score combination.]: We consider three possible methods for

@@

    the tree, and then computes a global $F$ score.

@@

To avoid this conflation, on the HTER corpora we report correlations
on $\bar{\mu}(m)$
and $\bar{\mu}(\textrm{HTER})$ (rather than measure $m$ and HTER), where
$\bar{\mu}$ represents mean-removal:
\begin{equation}
  \label{eq:meansub}
  \bar{\mu}(m(t_i)) = m(t_i) - \sum_{j=1}^I\frac{m(t_j)}{I}
\end{equation}
Mean-removal lowers the correlation $r$ values reported but ensures
that the reported correlations are among differences in the
translations rather than among differences in the underlying segments.
\footnote{ Previous work \cite{kahn08metricsmatr} reported HTER
  correlations against pairwise differences among translation segments
  derived from the same source segment. The results are similar to
  those reported here. However, we believe that pairwise differences
  introduce problems with the independence assumptions in
  the Pearson's $r$ tests, and we use mean-removal
  throughout this work instead.}

%% MO: Okay, but a little hard to figure out.
When reporting HTER correlations per-sentence, we use length-weighted
correlation, since unweighted correlations effectively puts too much
emphasis on short sentences.  We do not weight for length for the
per-document correlations in section~\ref{sec:hter1}, because we
assume documents to be equally important (regardless of length).
